---
title: "Task1"
author: "BasonCamille"
date: "13/09/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(httr)
#install.packages("rjstat")
library(rjstat)
library(lubridate)
#Dinstall.packages("stringr", dependencies=TRUE)
library(stringr)


```
## Importation of dataset

```{r}
csv_counties <- "http://data.ssb.no/api/v0/dataset/95274.json?lang=no"
csv_countries <- "http://data.ssb.no/api/v0/dataset/95276.json?lang=no"
counties <- GET(csv_counties)
countries <- GET(csv_countries)
counties <- fromJSONstat(content(counties, "text"))
countries <- fromJSONstat(content(countries, "text"))
counties <- counties[[1]]
countries <- countries[[1]]
```
## Change as date the countrie dataset

```{r}
countries$måned <- as.character(countries$måned)
countries$måned <-as.Date(paste(str_sub(countries$måned, 1, 4), str_sub(countries$måned, 6, 8), 1, sep="-"), "%Y-%m-%d")

```
## Change as date the countie dataset

```{r}
counties$måned <- as.character(counties$måned)
counties$måned <-as.Date(paste(str_sub(counties$måned, 1, 4), str_sub(counties$måned, 6, 8), 1, sep="-"), "%Y-%m-%d")
```
## Change the countries label

```{r}
countries$statistikkvariabel <- recode(countries$statistikkvariabel, "Kapasitetsutnytting av senger (prosent)" = "Beds percentage capacity utilization", "Kapasitetsutnytting av rom (prosent)" = "Rooms percentage capacity utilization","Pris per rom (kr)" =	"Price per room (kr)" )
```
## Change the counties label
```{r}
counties$statistikkvariabel <- recode(counties$statistikkvariabel, "Kapasitetsutnytting av senger (prosent)" = "Beds percentage capacity utilization", "Kapasitetsutnytting av rom (prosent)" = "Rooms percentage capacity utilization","Pris per rom (kr)" =	"Price per room (kr)" )

```
## Merge the two dataframe
```{r}
mix <- rbind(countries, counties)
```

## Calculate average room price

```{r}
mix$month <- format(mix$måned,"%m")

dataCountrie <- mix %>% filter (region=="Hele landet", value !=0.0 , statistikkvariabel == "Price per room (kr)" ) %>% group_by(month) %>% summarize(mean_room_countrie=mean(value))

dataCountie <- mix %>% filter (region!="Hele landet", value !=0.0 , statistikkvariabel == "Price per room (kr)" ) %>% group_by(month) %>% summarize(mean_room_countie=mean(value))
  
```
## Average room price in the countrie by month 
```{r}
print(dataCountrie)
```
## Average room price in the counties by month 
```{r}
print(dataCountie)
```
## Difference of room price in the counties and in the countrie

```{r}
dif <- left_join(dataCountrie,dataCountie, by="month")
dif$difference <- dif$mean_room_countrie - dif$mean_room_countie
print(dif)
```
## Difference of room price by counties and by countrie
```{r}
meanCountie <- mix %>% filter (value !=0.0 , statistikkvariabel == "Price per room (kr)" ) %>% group_by(region) %>% summarize(mean_room_countie=mean(value))

meanCountrie <- meanCountie %>% filter(region=="Hele landet") %>% select(mean_room_countie)
meanCountrie <- as.numeric(meanCountrie)
meanCountie$difference <- meanCountie$mean_room_countie - meanCountrie
print(meanCountie)
highest_pos <- max(meanCountie$difference)
highest_pos <- meanCountie %>% filter(difference==highest_pos) %>% select(region)
highest_neg <- min (meanCountie$difference)
highest_neg <- meanCountie %>% filter(difference==highest_neg) %>% select(region)
```
The highest positive difference in price is the region `r highest_pos` and the highest negative difference in price is in `r highest_neg`. 

# Highest positive and negative difference per county and per year
```{r}
mix$year <- format(mix$måned,"%Y")
meanCountieByYears <- mix %>% filter (region!="Hele landet" , value !=0.0 , statistikkvariabel == "Price per room (kr)") %>% group_by(region, year) %>% summarize(mean_room_countie=mean(value))
meanCountieByYears$difference <- meanCountieByYears$mean_room_countie - meanCountrie
highest_pos <- max(meanCountieByYears$difference)
highest_pos_RegionYear <- meanCountieByYears %>% filter(difference==highest_pos) %>% select(region, year)
highest_neg <- min (meanCountieByYears$difference)
highest_neg_RegionYear <- meanCountieByYears %>% filter(difference==highest_neg) %>% select(region, year)

```
The highest positive difference in price is the region `r highest_pos_RegionYear` and the highest negative difference in price are in `r highest_neg_RegionYear`.

## Plot of the monthly price difference for Troms county from 1999 until today
```{r}
priceTroms <- mix %>% filter (region=="Troms - Romsa", year>1998, value !=0.0 , statistikkvariabel == "Price per room (kr)") %>% group_by(month)%>% summarize(mean_room_countie=mean(value))
priceTroms$difference <- priceTroms$mean_room_countie - meanCountrie

plot( x= priceTroms$month, y = priceTroms$difference,cex.lab=0.75, cex.main=0.75, type = "l", col="blue",
     xlab="Month", 
     ylab="Room price difference", 
     main="Difference of average country's room price compared to average counties's room price by month")

```

## Relationship between room capacity and price since January 2010 per connties

```{r}
roomCapacity <- mix %>% filter(year>2009, statistikkvariabel =="Rooms percentage capacity utilization", value !=0.0) %>% group_by(region,year) %>% summarize(mean_capacity=mean(value))
ggplot(data = roomCapacity, aes(x=year, y=mean_capacity, group=region)) + 
   geom_line(aes(col=region)) + labs(title="Room capacity percentage per years",
       x="Year", y = "Capacity(%)")

roomPrice <- mix %>% filter(year>2009, statistikkvariabel =="Price per room (kr)", value !=0.0) %>% group_by(region,year) %>% summarize(mean_price=mean(value))
ggplot(data = roomPrice, aes(x=year, y=mean_price, group=region)) + 
   geom_line(aes(col=region)) + labs(title="Room price per years",
       x="Year", y = "Price (kr)")


```

It seems that the price of rooms and their capacity are correlated. But it is difficult to say with these graphics. We need to study a few regions in particular.

## Comparaison with Akershus regions

```{r}
compare <- merge(roomPrice,roomCapacity,by=c("region","year"))

Akershus <- compare %>% filter(region=="Akershus")

ggplot(data = Akershus, aes(x=year, y=mean_price, group=region)) + 
   geom_line(aes(col=region)) + labs(title="Price room at Akershus",
       x="Year", y="Price")
ggplot(data = Akershus, aes(x=year, y=mean_capacity, group=region)) + 
   geom_line(aes(col=region)) + labs(title="Capacity room at Akershus",
       x="Year", y="Capacity")

```

## Comparaison with Aust-Agder regions

```{r}


Aust<- compare %>% filter(region=="Aust-Agder")

ggplot(data = Aust, aes(x=year, y=mean_price, group=region)) + 
   geom_line(aes(col=region)) + labs(title="Price room at Aust-Agder",
       x="Year", y="Price")
ggplot(data = Aust, aes(x=year, y=mean_capacity, group=region)) + 
   geom_line(aes(col=region)) + labs(title="Capacity room at Aust-Agder",
       x="Year", y="Capacity")

```

## Comparaison with Buskerud regions
```{r}

Buskerud <- compare %>% filter(region=="Buskerud")

ggplot(data =Buskerud, aes(x=year, y=mean_price, group=region)) + 
   geom_line(aes(col=region)) + labs(title="Price room at Buskerud",
       x="Year", y="Price")
ggplot(data = 	Buskerud, aes(x=year, y=mean_capacity, group=region)) + 
   geom_line(aes(col=region)) + labs(title="Capacity room at Buskerud",
       x="Year", y="Capacity")

```

## Comparaison with Finnmark - Finnmárku regions
```{r}

Finnmark <- compare %>% filter(region=="Finnmark - Finnmárku")

ggplot(data =	Finnmark, aes(x=year, y=mean_price, group=region)) + 
   geom_line(aes(col=region)) + labs(title="Price room at 	Finnmark - Finnmárku",
       x="Year", y="Price")
ggplot(data = Finnmark, aes(x=year, y=mean_capacity, group=region)) + 
   geom_line(aes(col=region)) + labs(title="Capacity room at 	Finnmark - Finnmárku",
       x="Year", y="Capacity")

```

## Comparaison with 	Hedmarkregions
```{r}

Hedmark <- compare %>% filter(region=="Hedmark")

ggplot(data =Hedmark, aes(x=year, y=mean_price, group=region)) + 
   geom_line(aes(col=region)) + labs(title="Price room at 	Hedmark",
       x="Year", y="Price")
ggplot(data = Hedmark, aes(x=year, y=mean_capacity, group=region)) + 
   geom_line(aes(col=region)) + labs(title="Capacity room at 	Hedmark",
       x="Year", y="Capacity")

```

## Comparaison with Nordland regions
```{r}

Nordland <- compare %>% filter(region=="Nordland")

ggplot(data =Nordland, aes(x=year, y=mean_price, group=region)) + 
   geom_line(aes(col=region)) + labs(title="Price room at Nordland",
       x="Year", y="Price")
ggplot(data = Nordland, aes(x=year, y=mean_capacity, group=region)) + 
   geom_line(aes(col=region)) + labs(title="Capacity room at Nordland",
       x="Year", y="Capacity")

```

To conclude the price room and the capacity seem correlated. 
